A Paucity of Young Stars and Planets in the Kepler Field

### 2024-06-05 paper/ms.tex
update details

Young ($<$1\,Gyr) exoplanets represent one means of building
the timeline for exoplanet evolution.  Informative individual
exemplars include V1298~Tau, a resonant chain of 
puffy planets that is a likely precusor to the compact
multiplanet systems \citep{David_2019}, and HIP~67522, a Jupiter-sized
planet with a sub-Neptunian mass (\citealt{Rizzuto_2020}; Thao et
al.~submitted).  Population-level analyses have similarly suggested
differences in the size distribution of young exoplanets relative to
their older counterparts
\citep{Berger_2020b_rpage,David_2021,Sandoval_2021,2023AJ....166..248C,2024arXiv240303261V}.

@@

Despite Kepler's main mission ending quite some time ago, the ages of
many Kepler planets remain uncertain.  While isochrone ages have been
calculated for Kepler stars \citep{Berger_2020b_rpage} and Kepler
Objects of Interest \citep[KOIs;][]{Petigura_2022}, such ages are
most precise for stars whose luminosities and temperatures separate
them from the main sequence.  For $\lesssim$1\,Gyr stars, isochrone
ages are therefore limited.

@@

\begin{figure}[!t]
	\begin{center}
		\subfloat{
			\includegraphics[width=0.48\textwidth]{st_params_M_G_vs_dr3_bp_rp.pdf}
		}

		\vspace{-0.3cm}
		\subfloat{
			\includegraphics[width=0.48\textwidth]{st_params_adopted_logg_vs_adopted_Teff.pdf}
		}
	\end{center}
	\vspace{-0.5cm}
  \caption{{\bf The stars.}  Our analysis focuses on stars observed by
  Kepler with previously reported rotation periods (gray points).  The
  rotation periods are primarily drawn from
  \citet{Santos_2019,Santos_2021}.  About half of these rotators are
  suitable for gyrochronology (dark gray points), based on factors
  including their non-binarity and proximity to the main
  sequence (see Section~\ref{subsec:flags}).  Some
  host ``confirmed'' or ``candidate'' KOIs that meet additional
  planetary quality criteria (yellow points;
  Section~\ref{subsec:plflags}).  Surface gravities and effective
  temperatures were derived photometrically by
  \citet{Berger_2020a_catalog}.  Isochrones in the lower panel are
  from MIST \citep{Choi_2016}.
	}
	\label{fig:stellarprops}
\end{figure}

@@

\begin{figure*}[!t]
	\begin{center}
		\subfloat{
			\includegraphics[width=0.49\textwidth]{prot_teff_Santos19_Santos21_dquality.pdf}
		}
		\subfloat{
			\includegraphics[width=0.49\textwidth]{koi_mean_prot_teff_koi_X_S19S21dquality_keepgrazing.pdf}
		}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    {\bf Rotation periods for Kepler target stars (left) and known
    planet hosts (right)}.  
    The gray lines are ``mean fits'' to the slow rotation sequences of
    open clusters.  The stellar sample (left) includes only apparently
    single stars near the main sequence with $\log g$$>$4.2,
    RUWE$<$1.4, and temperatures of 3800--6200\,K.  The color map has
    a linear stretch.  The planet-hosts (right) require the same
    stellar cuts, and include only the confirmed and candidate planets
    described in Section~\ref{subsec:plflags}.  An order of magnitude
    estimate for the number of young planets discovered by Kepler
    follows by counting planets below the mean rotational isochrones.
	}
	\label{fig:prot_vs_teff}
\end{figure*}

>>>>

Young ($<$1\,Gyr) exoplanets represent one means of building
the timeline for exoplanet evolution.  Informative individual
exemplars include V1298~Tau, a resonant chain of 
puffy planets that is a likely precusor to the compact
multiplanet systems \citep{David_2019}, and HIP~67522b, a Jupiter-sized
planet with a sub-Neptunian mass (\citealt{Rizzuto_2020}; Thao et
al.~submitted).  Population-level analyses have similarly suggested
differences in the size distribution of young exoplanets relative to
their older counterparts
\citep{Berger_2020b_rpage,David_2021,Sandoval_2021,2023AJ....166..248C,2024arXiv240303261V}.

@@

Despite Kepler's main mission ending quite some time ago, the ages of
many Kepler planets remain uncertain.  While isochrone ages have been
calculated for Kepler stars \citep{Berger_2020b_rpage} and Kepler
Objects of Interest \citep[KOIs;][]{Petigura_2022}, such ages are
most precise for stars whose luminosities and temperatures separate
them from the main sequence.  For 0.1--1\,Gyr stars that are on
the main sequence, isochrone ages are therefore limited.

@@

\begin{figure}[!t]
	\begin{center}
		\subfloat{
			\includegraphics[width=0.47\textwidth]{st_params_M_G_vs_dr3_bp_rp.pdf}
		}

		\vspace{-0.3cm}
		\subfloat{
			\includegraphics[width=0.47\textwidth]{st_params_adopted_logg_vs_adopted_Teff.pdf}
		}
	\end{center}
	\vspace{-0.5cm}
  \caption{{\bf The stars.}  Our analysis focuses on stars observed by
  Kepler with previously reported rotation periods (gray points).  The
  rotation periods are primarily drawn from
  \citet{Santos_2019,Santos_2021}.  About half of the stars with
  rotation periods are
  suitable for gyrochronology (dark gray points), based on factors
  including their non-binarity and proximity to the main
  sequence (orange line in lower panel; see Section~\ref{subsec:flags}).  Some
  host ``confirmed'' or ``candidate'' KOIs that meet additional
  planetary quality criteria (yellow points;
  Section~\ref{subsec:plflags}).  Surface gravities and effective
  temperatures were derived photometrically by
  \citet{Berger_2020a_catalog}.  Isochrones in the lower panel are
  from MIST \citep{Choi_2016}.
	}
	\label{fig:stellarprops}
\end{figure}

@@

\begin{figure*}[!t]
	\begin{center}
		\subfloat{
			\includegraphics[width=0.49\textwidth]{prot_teff_Santos19_Santos21_dquality.pdf}
		}
		\subfloat{
			\includegraphics[width=0.49\textwidth]{koi_mean_prot_teff_koi_X_S19S21dquality_keepgrazing.pdf}
		}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    {\bf Rotation periods for Kepler target stars (left) and known
    planet hosts (right)}.  
    The gray lines are ``mean fits'' to the slow rotation sequences of
    open clusters.  The stellar sample (left) includes only apparently
    single stars near the main sequence with $\log g$$>$4.2,
    RUWE$<$1.4, and temperatures of 3800--6200\,K.  
    The planet-hosts (right) require the same
    stellar cuts, and include only the confirmed and candidate planets
    described in Section~\ref{subsec:plflags}.  The number of planets $N_{\rm p}$
    and number of stars $N_{\rm s}$ are noted in each panel.
    An order of magnitude
    estimate for the number of young planets discovered by Kepler
    follows by counting planets below the mean rotational isochrones.
	}
	\label{fig:prot_vs_teff}
\end{figure*}
